A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-25 text/conclusion.tex
Fix typo.

We have proposed a new multi-stage calculus \LMD with dependent types,
which make it possible for programmers to express finer-grained
properties about the behavior of code values.  The combination leads
to augmentation of almost all judgments in the type system with stage
information.  CSP and type equivalence specially tailored for it are
keys to expressing dependently typed practical code generators.  We
have proved basic properties of \LMD, including preservation,
confluence, strong normalization for full reduction, and progress for
staged reduction.

Developing a typechecking algorithmic for \LMD is left for future
work.  We expect that most of the development is straigtforward,
except for implicit CSP at the type-level and \%-erasing equivalence
rules.

>>>>

We have proposed a new multi-stage calculus \LMD with dependent types,
which make it possible for programmers to express finer-grained
properties about the behavior of code values.  The combination leads
to augmentation of almost all judgments in the type system with stage
information.  CSP and type equivalence (specially tailored for CSP) are
keys to expressing dependently typed practical code generators.  We
have proved basic properties of \LMD, including preservation,
confluence, strong normalization for full reduction, and progress for
staged reduction.

Developing a typechecking algorithm for \LMD is left for future
work.  We expect that most of the development is straigtforward,
except for implicit CSP at the type-level and \%-erasing equivalence
rules.
